---
title: "Study 3 -- Similarity Over Time"
subtitle: "Conversational Linguistic Features Predict Social Network Learning"
author: "Helen Schmidt"
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
    theme: cerulean
    toc: yes
    toc_float: yes
    code_folding: hide
---
<style>
h1, h2, h3, h4, h5, h6, legend {
    color: #1c3aa9;
}
</style>

```{r warning = FALSE, message = FALSE, echo = FALSE, include = FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
library(ggplot2)
library(tidytext)
library(readr)
library(knitr)
library(wordcloud)
library(wordcloud2)
library(RColorBrewer)
library(tm)
library(SnowballC)
library(XML)
library(RCurl)
library(ggpubr)
library(wesanderson)
library(reshape2)
library(MetBrewer)
library(sentimentr)
library(sna)
library(splitstackshape)
library(GGally)
library(ggraph)
library(gutenbergr)
library(igraph)
library(Matrix)
library(network)
library(tidygraph)
library(tibble)
library(formattable)
library(forcats)
library(lme4)
library(ggthemes)
library(lmerTest)
library(misty)
library(Rmisc)
library(effects)
library(arm)
library(stringr)
library(sjPlot)
library(lattice)
library(devtools)
library(sjmisc)
library(ggeffects)
library(reghelper)
library(glmmTMB)
library(reactable)
library(reactablefmtr)
library(tidyr)
library(dplyr)
library(janitor)
library(skimr)
library(corrplot)
library(bmlm)
library(stargazer)
library(patchwork)
```

Set up themes and notebook-wide settings. 

```{r}
# set up themes and notebook-wide settings
my.alpha = .2
colors <- c("#2185c5ff","#ff9715ff","#f20253ff","#7ecefdff","#1c3aa9ff")
fr.colors <- c(colors[2], colors[3])
se <- function(x) sqrt(var(x)/length(x))  #function to calculate SE
```

Set global working directory.

```{r, setup, include = FALSE}
# set global wd 
knitr::opts_knit$set(root.dir = "/Volumes/GoogleDrive/My Drive/SANLab/Experiments/Survivor-Language/Analysis/") 
# set to 3 decimal places for entire markdown
options(digits = 10)
```

# Similarity over whole season

% time chosen values are mean-centered at the dyad level.

## Friends

```{r}
# load friendship dyad data frame
df <- read.csv("./Paper-Analysis/data/friend-dyads.csv")

# add dyad pair column
df <- data.frame(df, stringsAsFactors = F) %>%
  mutate(dyad = paste0(pmin(Target,ChoiceOption), pmax(Target,ChoiceOption), sep="")) 

# ONLY include dyads who are in the same tribe (SameTribe = 1)
sim <- subset(df, SameTribe == 1)
# only include similarity, time, dyad name
sim <- sim[,c(11,7,16)]

# remove duplicate similarity rows
sim <- distinct(sim, Time, dyad, .keep_all = T)

# correlate time with similarity
corr <- sim %>%
  group_by(dyad) %>%
    mutate(correlation = cor(similarity,Time))

# get mean % time per PID chosen from friend choices (collapse across clips)
friends <- df %>%
  group_by(PID, dyad, condType) %>%
    summarize(TimeChosen = mean(DyadPercentTimeChosen))

# This pipe gives a friendly warning:
# `summarise()` has grouped output by 'PID', 'dyad'. You can override using the `.groups` argument.
# This is not an issue, it's just telling me what columns I'm grouping by before summarizing.

# combine with % time chosen as friends from friends.choices
friend.corr <- merge(corr, friends, by = "dyad")

# remove friends & sim data frames
rm(friends)
rm(sim)
```

## Rivals

```{r}
# load rivalry dyad data frame
df <- read.csv("./Paper-Analysis/data/rival-dyads.csv")

# add dyad pair column
df <- data.frame(df, stringsAsFactors = F) %>%
  mutate(dyad = paste0(pmin(Target,ChoiceOption), pmax(Target,ChoiceOption), sep="")) 

# ONLY include dyads who are in the same tribe (SameTribe = 1)
sim <- subset(df, SameTribe == 1)
# only include similarity, time, dyad name
sim <- sim[,c(11,7,16)]

# remove duplicate similarity rows
sim <- distinct(sim, Time, dyad, .keep_all = T)

# correlate time with similarity
corr <- sim %>%
  group_by(dyad) %>%
    mutate(correlation = cor(similarity,Time))

# get mean % time per PID chosen from friend choices (collapse across clips)
rivals <- df %>%
  group_by(PID, dyad, condType) %>%
    summarize(TimeChosen = mean(DyadPercentTimeChosen))

# This pipe gives a friendly warning:
# `summarise()` has grouped output by 'PID', 'dyad'. You can override using the `.groups` argument.
# This is not an issue, it's just telling me what columns I'm grouping by before summarizing.

# combine with % time chosen as friends from friends.choices
rival.corr <- merge(corr, rivals, by = "dyad")

# remove friends & sim data frames
rm(rivals)
rm(sim)
```

## Model setup

**Note: I do not mean center % time chosen because it is constrained between 0 and 1 (can't have negative % time chosen).**

```{r}
# combine all correlations for friendship and rivalry
corr <- rbind(friend.corr, rival.corr)
names(corr)[7] <- "PercentChosen"

write.csv(corr, "./Paper-Analysis/data/friends_rivals_dyads.csv")

# make condType a factor
corr$condType <- as.factor(corr$condType)

# print number of similarity assessments
assessments <- corr %>%
  group_by(dyad, Time, condType) %>% # include number of dyads at each time point per condType
  summarize(similarityCount = mean(similarity))

numObs <- nrow(assessments)
print(paste0("Number of similarity assessments (count per condition type and time point) = ", numObs, sep = ""))

# run overall linear regression
# how is the similarity per dyad predicted by percent chosen as friends/rivals in episode 13 and time?
# three way interaction between % time chosen, condition type (friend/rival), and time
model1.wholeSeason <- lmer(similarity ~ PercentChosen * condType * Time + (1|PID) + (1|dyad),
                           data = corr)

# Singularity is a confirmed non-issue resolved with Bayesian approach. See supplemental section.

# summarize model
summary(model1.wholeSeason)

# get confidence intervals
confint(model1.wholeSeason)
# get simple slopes
simple_slopes(model1.wholeSeason)

# get -1SD slope, mean slope, +1SD slope to plot similarity X time
simple_slopes(model1.wholeSeason) %>%
  filter(Time == "sstest")

# plot 
plot_model(model1.wholeSeason, type = "pred",
          terms = c("Time","PercentChosen","condType"))

# plot_model(model1.wholeSeason, type = "int",
#            mdrt.values = "meansd")

# Using summarize in this chunk gives the following messages:
# `summarise()` has grouped output by 'dyad', 'Time'. You can override using the `.groups` argument.
# This is not an issue, it is just telling me which columns I've grouped by before summarizing.

```

## Plot!

```{r}
# ggpredict
model.df <- ggpredict(model1.wholeSeason, ci.lvl = 0.95,
                      terms = c("Time","PercentChosen","condType"))
model.df <- as.data.frame(model.df)

# plot results!
friend.df <- subset(model.df, facet == "Friend")
rival.df <- subset(model.df, facet == "Rival")

# 3 color gradient with friend and rival colors
friend.color.gradient <- c("#ffbf70",fr.colors[1],"#cc7000")
rival.color.gradient <- c("#fd4985",fr.colors[2],"#a20237")

# friend condition, x axis = time, y axis = similarity, group = percent chosen as friends
ggplot(friend.df, aes(x = x, y = predicted, color = group, fill = group)) +
  geom_line(size = 1.5) +
  geom_ribbon(alpha = .15,
              aes(ymin = conf.low, ymax = conf.high),
              linetype = .5) +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 11)) +
  scale_fill_manual(labels = c("0.29 (-1 SD)", "0.5 (mean)", "0.71 (+1 SD)"),
                      values = friend.color.gradient, name = "% time chosen") +
  scale_color_manual(labels = c("0.29 (-1 SD)", "0.5 (mean)", "0.71 (+1 SD)"),
                       values = friend.color.gradient, name = "% time chosen") +
  xlab("Time") +
  ylab("dyadic semantic similarity") +
  theme_classic() +
  theme(legend.position = "right",
        panel.background = element_blank(),
        axis.title.x = element_text(vjust = -0.4, size = 16),
        axis.title.y = element_text(vjust = 1.5, size = 16), 
        axis.text = element_text(size = 12),
        legend.text = element_text(size = 10),
        legend.title = element_text(size = 12))

friend <- last_plot()

# rival condition, x axis = time, y axis = similarity, group = percent chosen as friends
ggplot(rival.df, aes(x = x, y = predicted, color = group, fill = group)) +
  geom_line(size = 1.5) +
  geom_ribbon(alpha = .15,
              aes(ymin = conf.low, ymax = conf.high),
              linetype = .5) +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 11)) +
  scale_fill_manual(labels = c("0.29 (-1 SD)", "0.5 (mean)", "0.71 (+1 SD)"),
                      values = rival.color.gradient, name = "% time chosen") +
  scale_color_manual(labels = c("0.29 (-1 SD)", "0.5 (mean)", "0.71 (+1 SD)"),
                       values = rival.color.gradient, name = "% time chosen") +
  xlab("Time") +
  ylab("dyadic semantic similarity") +
  theme_classic() +
  theme(legend.position = "right",
        panel.background = element_blank(),
        axis.title.x = element_text(vjust = -0.4, size = 16),
        axis.title.y = element_text(vjust = 1.5, size = 16), 
        axis.text = element_text(size = 12),
        legend.text = element_text(size = 10),
        legend.title = element_text(size = 12))

rival <- last_plot()

# plot together and save!
friend | rival

ggsave(filename = "Study3-multiplot.jpeg",
       path = "/Volumes/GoogleDrive/My Drive/SANLab/Manuscripts/Survivor+Language/MarkdownFigures",
       width = 10, height = 5,
       units = c("in"))

ggsave(filename = "Study3-multiplot.pdf",
       path = "/Volumes/GoogleDrive/My Drive/SANLab/Manuscripts/Survivor+Language/MarkdownFigures",
       width = 10, height = 5,
       units = c("in"))

```

### Compare interaction model

```{r}
# run multilevel model
model.wholeSeason <- lmer(similarity ~ PercentChosen * condType * Time + (1|PID) + (1|dyad),
                           data = corr)
# run main effect model (null)
null.wholeSeason <- lmer(similarity ~ PercentChosen + condType + Time + (1|dyad) + (1|PID),
                        data = corr)

anova(model.wholeSeason, null.wholeSeason)

```

## Standardized Betas

```{r}
# standardize similarity, PercentChosen, and Time
corr$similarityZ <- as.numeric(scale(corr$similarity))
corr$PercentChosenZ <- as.numeric(scale(corr$PercentChosen))
corr$TimeZ <- as.numeric(scale(corr$Time))

model.wholeSeason <- lmer(similarityZ ~ PercentChosenZ * condType * TimeZ + (1|PID) + (1|dyad),
                           data = corr)
summary(model.wholeSeason)
confint(model.wholeSeason)
simple_slopes(model.wholeSeason)

null.wholeSeason <- lmer(similarityZ ~ PercentChosenZ + condType + TimeZ + (1|dyad) + (1|PID),
                        data = corr)

anova(model.wholeSeason, null.wholeSeason)

```


# Supplemental: Bayesian approach to examine singularity

We took a Bayesian approach in order to establish that singularity would not undermine the validity of the models. Singularity typically occurs when there is limited variability within the random effects term(s) and/or the random effects structure is overly-complex relative to the variability offered by the data. Given the nature of our data, we opted to retain our random effects in all frequentist models after examining the same models with a Bayesian approach (using uninformative/default priors, which should, and do, yield the same beta estimates as a frequentist approach).

## Similarity
```{r brms1}
colors <- c("#2185c5ff","#ff9715ff","#f20253ff","#7ecefdff","#1c3aa9ff")
fr.colors <- c(colors[2], colors[3])

# 3 color gradient with friend and rival colors
friend.color.gradient <- c("#ffbf70",fr.colors[1],"#cc7000")
rival.color.gradient <- c("#fd4985",fr.colors[2],"#a20237")

library(bayesplot)
library(brms)
library(tidybayes)
library(interactions)

model1.wholeSeason.brms <- brm(data = corr,
      family = gaussian,
      similarity ~ PercentChosen * condType * Time + (1|PID) + (1|dyad), 
      iter = 4000, warmup = 1500, chains = 3, cores = 3,
      control = list(adapt_delta = .999, max_treedepth = 15), 
      seed = 9)

summary(model1.wholeSeason.brms, waic = TRUE)
conditional_effects(model1.wholeSeason.brms)
pairs(model1.wholeSeason.brms)
plot(model1.wholeSeason.brms)

interactions::interact_plot(model = model1.wholeSeason.brms,
                            pred = Time,
                            modx = PercentChosen,
                            mod2 = condType,
                            data = corr)

model1.wholeSeason.brms %>% 
  neff_ratio() %>% 
  mcmc_neff_hist(binwidth = .1) +
  yaxis_text()

#main effect model for comparison
model1.wholeSeason.brms.main <- brm(data = corr,
      family = gaussian,
      similarity ~ PercentChosen + condType + Time + (1|PID) + (1|dyad), 
      iter = 4000, warmup = 1500, chains = 3, cores = 3,
      control = list(adapt_delta = .999, max_treedepth = 15), 
      seed = 9)
#model comparison via loo
model1.wholeSeason.brms <- add_criterion(model1.wholeSeason.brms, "loo")
model1.wholeSeason.brms.main <- add_criterion(model1.wholeSeason.brms.main, "loo")
loo_compare(model1.wholeSeason.brms, model1.wholeSeason.brms.main) %>% 
  print(simplify = F)
```

```{r}
#plot!
sim_int <- interactions::interact_plot(model = model1.wholeSeason.brms,
                            pred = Time,
                            modx = PercentChosen,
                            mod2 = condType,
                            data = corr,
                            interval = T)

sim_int <- as.data.frame(sim_int$data)
friend_int <- subset(sim_int, mod2_group == "condType = Friend")
rival_int <- subset(sim_int, mod2_group == "condType = Rival")

# friend plot
ggplot(friend_int, aes(x = Time, y = similarity, color = modx_group, fill = modx_group)) +
  geom_line(size = 1.5) +
  geom_ribbon(alpha = .15,
              aes(ymin = ymin, ymax = ymax),
              linetype = .5) +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 11)) +
  scale_fill_manual(labels = c("0.29 (-1 SD)", "0.5 (mean)", "0.71 (+1 SD)"),
                      values = friend.color.gradient, name = "% time chosen") +
  scale_color_manual(labels = c("0.29 (-1 SD)", "0.5 (mean)", "0.71 (+1 SD)"),
                       values = friend.color.gradient, name = "% time chosen") +
  xlab("Time") +
  ylab("dyadic semantic similarity") +
  theme_classic() +
  theme(legend.position = "right",
        panel.background = element_blank(),
        axis.title.x = element_text(vjust = -0.4, size = 16),
        axis.title.y = element_text(vjust = 1.5, size = 16), 
        axis.text = element_text(size = 12),
        legend.text = element_text(size = 10),
        legend.title = element_text(size = 12))

friend <- last_plot()

# rival plot
ggplot(rival_int, aes(x = Time, y = similarity, color = modx_group, fill = modx_group)) +
  geom_line(size = 1.5) +
  geom_ribbon(alpha = .15,
              aes(ymin = ymin, ymax = ymax),
              linetype = .5) +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 11)) +
  scale_fill_manual(labels = c("0.29 (-1 SD)", "0.5 (mean)", "0.71 (+1 SD)"),
                      values = rival.color.gradient, name = "% time chosen") +
  scale_color_manual(labels = c("0.29 (-1 SD)", "0.5 (mean)", "0.71 (+1 SD)"),
                       values = rival.color.gradient, name = "% time chosen") +
  xlab("Time") +
  ylab("dyadic semantic similarity") +
  theme_classic() +
  theme(legend.position = "right",
        panel.background = element_blank(),
        axis.title.x = element_text(vjust = -0.4, size = 16),
        axis.title.y = element_text(vjust = 1.5, size = 16), 
        axis.text = element_text(size = 12),
        legend.text = element_text(size = 10),
        legend.title = element_text(size = 12))

rival <- last_plot()

# plot together and save!
friend | rival

ggsave(filename = "Study3-bayes-multiplot.jpeg",
       path = "/Volumes/GoogleDrive/My Drive/SANLab/Manuscripts/Survivor+Language/MarkdownFigures",
       width = 10, height = 5,
       units = c("in"))

ggsave(filename = "Study3-bayes-multiplot.pdf",
       path = "/Volumes/GoogleDrive/My Drive/SANLab/Manuscripts/Survivor+Language/MarkdownFigures",
       width = 10, height = 5,
       units = c("in"))

```
